Viscous Transport in Eroding Porous Media

### 2019-06-20 docs/transport/erosion_transport.tex
do the result section in transport paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Transport, Tracers, and Tortuosity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Erosion leads to interesting porous geometries, and we are interested in
characterizing transport in these geometries.  To characterize the
transport, we first require tracer trajectories (streamlines) that are
governed by
\begin{align}
  \frac{d\ss}{dt} = \uu(\ss,t), \quad \ss(0) = \ss_0.
\end{align}
Instead of allowing the transport and erosion to happen simultaneously,
we freeze the geometry and compute the streamlines in this fixed
geometry.  Therefore, the velocity $\uu$ has no temporal dependence when
we characterize the transport.
{\color{red}
To study the interaction of fluid and fixed bodies in the porous media,
some parameters can be used to describle the interation quantitively,
for example the porosity, the permeability, and the tortuosity. 
The relation of porosity and tortuosity has been studied in~\cite{matyka2008tortuosity}.
The definition of porosity is the ratio 
$$\phi=\frac{A_v}{A_T}$$
where $A_v$ is the area of void-space and $A_T$ is the area of the calculating area.}
The tortuosity ...
{\color{red} represents the weighted average travel distance of a tracer in a porous media. 
The definition of tortuosity is 
$$T=\frac{1}{d}\frac{\displaystyle\int_{S}u_x(y) \lambda(y)dy}{\displaystyle\int_{S}u_x(y)dy}$$
where $S$ is an arbitrary cross section which is perpendicular to the x axis,
$\lambda(y)$ is the length of streamline at y on $S$, 
$u_x(y)$ is the component of velocity at y which is normal to $S$, and 
$d$ is the distance from $S$ to the end cross section.
It depends on not only the geometric structure but also the velocity of the fluid 
which is different from the porosity since porosity only depends on the geometric structure.}
{\color{red}Beisdes, the local tortuosity has been used to analysis 
the local behavior of steamline around a body
in~\cite{matyka2008tortuosity}.
The definition of local tortuosity of the tracers at $y$ on $S$ is
$$\tau(y)=\frac{\lambda(y)}{d}.$$ 
To calculate tortuosity $T$ numerically, we use the simple quaduature rule
$$T=\frac{1}{d}\frac{\displaystyle\sum_{i=1}^{N} u_x(y_i) \lambda(y_i) \Delta y_i}{\displaystyle\sum_{i=1}^{N} u_x(y_i) \Delta y_i},$$ 
where $y_i$ is the point on $S$ and $\Delta y_i = y_{i+1}-y_{i}$.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{100 bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
 \begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =0.9\linewidth]{./figs/100b_50}
\caption{100 bodies at t= 0.005}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =1.1\linewidth]{./figs/100b_100}
\caption{99 bodies at t= 0.01}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =0.9\linewidth]{./figs/100b_150}
\caption{94 bodies at t= 0.015}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =1.1\linewidth]{./figs/100b_200}
\caption{82 bodies at t= 0.02}
\end{subfigure}
\caption{\label{fig:Eroding100vort} Erosion of 100 bodies with the
  fixed-pressure-drop condition. The color is the vorticity of fluid. In
  this simulation, we use $N_\iin = 256$ discretization points on the
  body, $N_\out = 1024$ points on the outer wall, a time-step of
  $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and
  $\sigma=10/256$.}
\end{figure}

{\color{red}
This case is 100 bodies in a Hagen-Poiseuille flow. The background
flow is 
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right]
\end{align}
with floating flow rate $U$ such that pressure drop is fixed from x = -2 to x = 2.
We record the vorticity of 
fluid in colormap during the bodies erosion in Fig.~\ref{fig:Eroding100vort} and 
measure the gap sizes between bodies in Fig.~\ref{fig:Eroding100gap} at four equispaced times.
Since the vorticity is equivalent to the shear stress and the erosion is faster in the regions where
the magnitude of the vorticity is larger,

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/gap_hist100_50}
\caption{100 bodies with 318 gaps at t= 0.005}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/gap_hist100_100}
\caption{99 bodies with 312 gaps at t= 0.01}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/gap_hist100_150}
\caption{94 bodies with 294 gaps at t= 0.015}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/gap_hist100_200}
\caption{82 bodies with 254 gaps at t= 0.02}
\end{subfigure}
\caption{\label{fig:Eroding100gap} The histograms of gaps in the case of erosion of 100 bodies at four time steps.}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Transport, Tracers, and Tortuosity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Erosion leads to interesting porous geometries, and we are interested in
characterizing transport in these geometries.  To characterize the
transport, we first require tracer trajectories (streamlines) that are
governed by
\begin{align}
  \frac{d\ss}{dt} = \uu(\ss,t), \quad \ss(0) = \ss_0.
\end{align}
Instead of allowing the transport and erosion to happen simultaneously,
we freeze the geometry and compute the streamlines in this fixed
geometry.  Therefore, the velocity $\uu$ has no temporal dependence when
we characterize the transport.
{\color{red}
To study the interaction of fluid and fixed bodies in the porous media,
some parameters can be used to describle the interation quantitively,
for example the porosity, the permeability, and the tortuosity. 
The relation of porosity and tortuosity has been studied in~\cite{matyka2008tortuosity}.
The definition of porosity is the ratio 
$$\phi=\frac{A_v}{A_T}$$
where $A_v$ is the area of void-space and $A_T$ is the area of the calculating area.}
{\color{red} The tortuosity represents the weighted average travel distance of a tracer in a porous media. 
The definition of tortuosity is 
$$T=\frac{1}{d}\frac{\displaystyle\int_{S}u_x(y) \lambda(y)dy}{\displaystyle\int_{S}u_x(y)dy}$$
where $S$ is an arbitrary cross section which is perpendicular to the x axis,
$\lambda(y)$ is the length of streamline at y on $S$, 
$u_x(y)$ is the component of velocity at y which is normal to $S$, and 
$d$ is the distance from $S$ to the end cross section.
It depends on not only the geometric structure but also the velocity of the fluid 
which is different from the porosity since porosity only depends on the geometric structure.}
{\color{red}Beisdes, the local tortuosity~\cite{matyka2008tortuosity} has been used to analysis 
the local behavior of steamline around a body. 
The definition of local tortuosity of the tracers at $y$ on $S$ is
$$\tau(y)=\frac{\lambda(y)}{d}.$$ 
To calculate tortuosity $T$ numerically, we use the simple quaduature rule
$$T=\frac{1}{d}\frac{\displaystyle\sum_{i=1}^{N} u_x(y_i) \lambda(y_i) \Delta y_i}{\displaystyle\sum_{i=1}^{N} u_x(y_i) \Delta y_i},$$ 
where $y_i$ is the point on $S$ and $\Delta y_i = y_{i+1}-y_{i}$.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{100 bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
 \begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =0.9\linewidth]{./figs/100b_50}
\caption{100 bodies and porosity = 55.54\% at t= 0.005}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =1.1\linewidth]{./figs/100b_100}
\caption{99 bodies and porosity = 62.98\% at t= 0.01}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =0.9\linewidth]{./figs/100b_150}
\caption{94 bodies and porosity = 72.22\% at t= 0.015}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =1.1\linewidth]{./figs/100b_200}
\caption{82 bodies and porosity = 83.37\% at t= 0.02}
\end{subfigure}
\caption{\label{fig:Eroding100vort} Erosion of 100 bodies with the
  fixed-pressure-drop condition. The color is the vorticity of fluid. In
  this simulation, we use $N_\iin = 256$ discretization points on the
  body, $N_\out = 1024$ points on the outer wall, a time-step of
  $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and
  $\sigma=10/256$.}
\end{figure}

{\color{red}
This case is 100 bodies in a Hagen-Poiseuille flow. The background
flow is 
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right]
\end{align}
with floating flow rate $U$ such that pressure drop is fixed from x = -2 to x = 2.
We record the vorticity of 
fluid in colormap during the bodies erosion in Fig.~\ref{fig:Eroding100vort} and 
measure the gap sizes between bodies in Fig.~\ref{fig:Eroding100gap} at four equispaced times.
Since the vorticity is equivalent to the shear stress and the erosion is faster in the regions where
the magnitude of the vorticity is larger 
so the erosion is getting faster and faster 
from the first snapshot to the forth one in Fig.~\ref{fig:Eroding100vort}.
At t = 0.005 the porosity is 55.54\% and the most gap sizes between bodies are less than 0.015 in 
Fig.~\ref{fig:Eroding100gap}(a). Since some of the bodies are vanished in the fluid, the numner of gaps 
decreases and the gap sizes get larger and larger between the remaining bodies. 
In Fig.~\ref{fig:Eroding100gap}(b) and (c) we still can see small gap sizes are in the majority but 
it is not as concentrated as the one we see in  Fig.~\ref{fig:Eroding100gap}(a). 
\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/gap_hist100_50}
\caption{100 bodies with 318 gaps at t= 0.005}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/gap_hist100_100}
\caption{99 bodies with 312 gaps at t= 0.01}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/gap_hist100_150}
\caption{94 bodies with 294 gaps at t= 0.015}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/gap_hist100_200}
\caption{82 bodies with 254 gaps at t= 0.02}
\end{subfigure}
\caption{\label{fig:Eroding100gap} The histograms of gaps in the case of erosion of 100 bodies at four time steps.}
\end{figure}
